---
title: "Number of marriage licenses issued in Toronto from 2011 to 2024"
subtitle: "Marriage licenses"
author: 
  - Taejun Um
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "Number of marriages in Toronto has been barely changing for last 10 years. However, starting in 2020, pattern of marriages has been dramatically changed due to pandemic. In this paper, it can show that pattern of marriages licenses issued during pandemic to current time (2020-2024) converted to random cloud. This implies that pandemic ruined the marriage pattern in Toronto."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```


# Introduction

You can and should cross-reference sections and sub-sections. We use @talia, @opendatatorotno, and @rohan.

The remainder of this paper is structured as follows. @sec-mydatasection



# Data {#sec-mydatasection}

Some of our data is of penguins (@fig-marriage), from @palmerpenguins.

```{r}
#| label: Number of marriage license issued
#| fig-cap: Date
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```

This scatter plot shows the number of marriage licenses issued since 2011 to 2024 in Toronto. It shows regular cyclic pattern with some outliers until 2020.





# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


